Covariate analysis of CMC RNASeq data reprocessed with RSEM-feature counts workflow with GRCh38 (DLPFC with CQN normlaisation)

### 2018-09-26 code/Rmd/CMC_DLPFC_RSEM_GRCh38_CQN_ModSel.Rmd
Minor sanity changes

knit2synapse::knitToFolderEntity(file = "./CMC_DLPFC_RSEM_GRCh38_CQN_ModSel.Rmd",
                                 parentId ="syn9846623",
                                 entityName = 'DLPFC - RSEM - EXPECTED COUNTS - GRCh38 - CQN - Sparse Model')
```

@@

synapseLogin()

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "./CMC_DLPFC_RSEM_GRCh38_CQN_ModSel.Rmd",
                                          parentId ="syn9846623",
                                          folderName = 'DLPFC - RSEM - EXPECTED COUNTS - GRCh38 - CQN - Sparse Model')
```

@@
